\thesistitle

### 2019-07-23 sections/clonerefactor.tex
Showing equality arrays for the example

\begin{figure}[H]
\begin{parcolumns}{3}
\colchunk[1]{
\begin{javacode}
|\highlightYellow|doA();
|\highlightYellow|doB();
doC();
doC();
\end{javacode}}
\colchunk[2]{
\begin{javacode}
doD();
|\highlightYellow|doA();
|\highlightYellow|doB();
doD();
\end{javacode}}
\colchunk[3]{
\begin{javacode}
doE();
doE();
|\highlightYellow|doA();
|\highlightYellow|doB();
\end{javacode}}
\end{parcolumns}
\caption{One clone instance in a type 2R clone has a high variability.}
\label{fig:2rvariabilityhigh3}
\end{figure}

@@

\subsubsection{Convert Equality Array to Graph}

>>>>

\begin{figure}[H]
\begin{parcolumns}{3}
\colchunk[1]{
\begin{javacode}
|\highlightYellow|doA();
|\highlightYellow|doB();
doC();
doC();
\end{javacode}}
\colchunk[2]{
\begin{javacode}
doD();
|\highlightYellow|doA();
|\highlightYellow|doB();
doD();
\end{javacode}}
\colchunk[3]{
\begin{javacode}
doE();
doE();
|\highlightYellow|doA();
|\highlightYellow|doB();
\end{javacode}}
\end{parcolumns}
\caption{A small subset of nodes has a high variability.}
\label{fig:2rvariabilityhigh3}
\end{figure}

@@

\subsubsection{Convert Equality Array to Graph}
After the global threshold check has failed, we build a clone graph on basis of the equality arrays.

\begin{figure}[H]
\begin{parcolumns}{3}
\colchunk[1]{
\begin{javacode}
|\highlightYellow|doA(); //{1, 2}
|\highlightYellow|doB(); //{3, 2}
doC(); //{4, 2}
doC(); //{4, 2}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
doD(); //{5, 2}
|\highlightYellow|doA(); //{1, 2}
|\highlightYellow|doB(); //{3, 2}
doD(); //{5, 2}
\end{javacode}}
\colchunk[3]{
\begin{javacode}
doE(); //{6, 2}
doE(); //{6, 2}
|\highlightYellow|doA(); //{1, 2}
|\highlightYellow|doB(); //{3, 2}
\end{javacode}}
\end{parcolumns}
\caption{Cloned code fragments from figure \ref{fig:2rvariabilityhigh3} together with their equality arrays.}
\label{fig:2rvariabilityhigh4}
\end{figure}

In figure \ref{fig:2rvariabilityhigh4} we display the equality arrays for each of the lines of a code example with a complex distribution of cloned fragments.
